---
title: "hw6"
output: github_document
date: '2023-11-28'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Load necessary packages 

```{r}
library(tidyverse)
library(modelr)
library(purrr)
set.seed(1)
```

## problem 1 (0 points)

```{r}
## no work shown for this problem 
```

## problem 2

Run code chunk from the course website: 
```{r}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2022-01-01",
    date_max = "2022-12-31") |>
  mutate(
    name = recode(id, USW00094728 = "CentralPark_NY"),
    tmin = tmin / 10,
    tmax = tmax / 10) |>
  select(name, id, everything())
```

Use 5000 bootstrap samples and, for each bootstrap sample, produce estimates of these two quantities. Plot the distribution of your estimates, and describe these in words. Using the 5000 bootstrap estimates, identify the 2.5% and 97.5% quantiles to provide a 95% confidence interval for r̂ 2
 and log(β̂ 0∗β̂ 1)

```{r}
boot_straps = 
  weather_df |> 
  modelr::bootstrap(n = 5000)

boot_straps |> pull(strap) |> nth(1)

```

Drawing 5000 samples and establishing the 95% CI:
```{r}
boot_straps = 
  weather_df |> 
  modelr::bootstrap(n = 5000)|> 
  mutate(
    models = map(.x = strap, ~lm(tmax ~ tmin + prcp, data = .x)), 
    results = map(models, broom::tidy)) |> 
  select(-strap, -models) |> 
  unnest(results) |> 
  group_by(term) |> 
  select(.id, term, estimate) |>
  pivot_wider(
    names_from = "term",
    values_from = "estimate"
  ) |> 
  janitor::clean_names() |>
  filter(tmin*prcp > 0) |> 
  mutate(
    log_B = log(tmin*prcp) 
  ) |> 
  summarize(
    LL = quantile(log_B, c(.025), na.rm = TRUE),
    UL = quantile(log_B, c(.975), na.rm = TRUE) 
   )
```

Finding R^2: 
```{r}
boot_straps = 
  weather_df |> 
  modelr::bootstrap(n = 5000) |> 
  mutate(
    models = map(strap, ~lm(tmax ~ tmin + prcp, data = .x)),
    results = map(models, broom::glance)
  ) |> 
  select(-strap, -models) |> 
  unnest(results) |> 
  janitor::clean_names() |> 
  summarize(
    LL = quantile(r_squared, c(.025)),
    UL = quantile(r_squared, c(.975)) 
  )
```

Plots: 

```{r}
## r squared plot 

weather_df |> 
  modelr::bootstrap(n = 5000) |> 
  mutate(
    models = map(strap, ~lm(tmax ~ tmin + prcp, data = .x)),
    results = map(models, broom::glance)
  ) |> 
  select(-strap, -models) |> 
  unnest(results) |> 
  ggplot(aes(x = r.squared)) + geom_density() +
  labs(
    title = "R-squared Distribution"
  )

```

The distribution of R-squared appears to be normal, based on the shape of the graph. It is centered around 0.92, which suggests that about 92% of the variance is explained by the model. The 95% confidence interval for R-squared is given by the 'summarize(LL = quantile(r_squared, c(.025)),UL = quantile(r_squared, c(.975)))' line and is (0.888,0.941). 

```{r}
## log plot 

  weather_df |> 
  modelr::bootstrap(n = 5000)|> 
  mutate(
    models = map(.x = strap, ~lm(tmax ~ tmin + prcp, data = .x)), 
    results = map(models, broom::tidy)) |> 
  select(-strap, -models) |> 
  unnest(results) |> 
  group_by(term) |> 
  select(.id, term, estimate) |>
  pivot_wider(
    names_from = "term",
    values_from = "estimate"
  ) |> 
  janitor::clean_names() |>
  filter(tmin*prcp > 0) |> 
  mutate(
    log_B = log(tmin*prcp) 
  ) |> ggplot(aes(x = log_B)) + geom_density() +
  labs(
    title = "Beta Distribution"
  )

```

The distribution of the variable I called 'log_B' appears to also be normally distributed but with a negative skew and is centered around -5. The 95% confidence interval for log_B is given by the 'summarize(LL = quantile(log_B, c(.025), na.rm = TRUE),UL = quantile(log_B, c(.975), na.rm = TRUE)) line and is also (0.888,0.941)


## problem 3

Load and clean the data for regression analysis: 
```{r}
birthweight_data = 
  read_csv("birthweight.csv") |>  
  janitor::clean_names() |> 
  mutate(
    babysex = as.factor(babysex),
    frace = as.factor(frace),
    malform = as.factor(malform),
    mrace = as.factor(mrace)
  )

#nrow(birthweight_data)
#ncol(birthweight_data)
```
There are no missing rows or columns in this dataset. 


Propose a regression model for birthweight: 

```{r}
fit_birthweight = lm(bwt ~ smoken + pnumlbw + momage, data = birthweight_data)
fit_birthweight |>  broom::tidy()
```
I chose these variables for my model because I wanted to see how variables I was not familiar with affect birth weight. I already knew that smoking during pregnancy increases the risk of a newborn having a low birth weight, but I did not have any prior knowledge about how previous low birth weights and age of the mother at birth affected birth weight, if at all. Because of this, I wanted to explore the relationship these variables have with birth weight. 


Show a plot of model residuals against fitted values – use add_predictions and add_residuals in making this plot: 

```{r}
birthweight_data |>  
  modelr::add_residuals(fit_birthweight) |> 
  modelr::add_predictions(fit_birthweight) |>  
  ggplot(aes(x = pred, y = resid)) + 
  geom_point() +
  labs(
    title = "Residuals vs Fitted Values",
    x = "Fitted",
    y = "Residuals"
    ) 
```

Compare your model to two others:

```{r}
fit_birthweight2 = lm(bwt ~ + blength + gaweeks, data = birthweight_data)

fit_birthweight3 = lm(bwt ~ bhead + bhead * blength * babysex, data = birthweight_data) 
```

Make this comparison in terms of the cross-validated prediction error; use crossv_mc and functions in purrr as appropriate: 

```{r}
cv_df = 
  crossv_mc(birthweight_data, 100) |> 
  mutate(
    train = map(train, as_tibble),
    test = map(test, as_tibble)
  )
```

```{r}
cv_df = 
  cv_df |>  
  mutate(
   mod_1 = map(.x = train, ~lm(bwt ~ smoken + pnumlbw + momage, data = .x)),
   mod_2 = map(.x = train, ~lm(bwt ~ + blength + gaweeks, data = .x)),
   mod_3 = map(.x = train, ~lm(bwt ~ bhead + bhead * blength * babysex, data = .x))
  ) |>  
  mutate(
    rmse_mod1 = map2_dbl(mod_1, .y = test, ~rmse(model = .x, data = .y)),
    rmse_mod2 = map2_dbl(mod_2, .y = test, ~rmse(model = .x, data = .y)),
    rmse_mod3 = map2_dbl(mod_3, .y = test, ~rmse(model = .x, data = .y))
  )
```

```{r}
cv_df |> 
  select(starts_with("rmse")) |> 
  pivot_longer(
    everything(),
    names_to = "model", 
    values_to = "rmse",
    names_prefix = "rmse_") |> 
  mutate(model = fct_inorder(model)) |> 
  ggplot(aes(x = model, y = rmse)) + geom_violin() +
  labs(
    title = "Comparison of the Three Models"
    ) 
```

