---
title: "hw6"
output: html_document
date: '2023-11-28'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## load necessary packages 

```{r}
library(tidyverse)
set.seed(1)
```

## problem 1 (0 points)

```{r}
## no work shown for this problem 
```

## problem 2

run code chunk from the course website: 
```{r}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2022-01-01",
    date_max = "2022-12-31") |>
  mutate(
    name = recode(id, USW00094728 = "CentralPark_NY"),
    tmin = tmin / 10,
    tmax = tmax / 10) |>
  select(name, id, everything())
```

Use 5000 bootstrap samples and, for each bootstrap sample, produce estimates of these two quantities. Plot the distribution of your estimates, and describe these in words. Using the 5000 bootstrap estimates, identify the 2.5% and 97.5% quantiles to provide a 95% confidence interval for r̂ 2
 and log(β̂ 0∗β̂ 1)

```{r}
boot_straps = 
  weather_df |> 
  modelr::bootstrap(n = 5000)

boot_straps |> pull(strap) |> nth(1)

```

Drawing 5000 samples and establishing the 95% CI:
```{r}
boot_straps = 
  weather_df |> 
  modelr::bootstrap(n = 5000)|> 
  mutate(
    models = map(.x = strap, ~lm(tmax ~ tmin + prcp, data = .x)), 
    results = map(models, broom::tidy)) |> 
  select(-strap, -models) |> 
  unnest(results) |> 
  group_by(term) |> 
  select(.id, term, estimate) |>
  pivot_wider(
    names_from = "term",
    values_from = "estimate"
  ) |> 
  janitor::clean_names() |>
  filter(tmin*prcp > 0) |> 
  mutate(
    log_B = log(tmin*prcp) 
  ) |> 
  summarize(
    LL = quantile(log_B, c(.025), na.rm = TRUE),
    UL = quantile(log_B, c(.975), na.rm = TRUE) 
  )
```

Finding R^2: 
```{r}
boot_straps = 
  weather_df |> 
  modelr::bootstrap(n = 5000) |> 
  mutate(
    models = map(strap, ~lm(tmax ~ tmin + prcp, data = .x)),
    results = map(models, broom::glance)
  ) |> 
  select(-strap, -models) |> 
  unnest(results) |> 
  janitor::clean_names() |> 
  summarize(
    LL = quantile(r_squared, c(.025)),
    UL = quantile(r_squared, c(.975)) 
  )
```

Plots: 
```{r}
## graph isnt showing up??
boot_straps = 
  weather_df |> 
  modelr::bootstrap(n = 5000)|> 
  mutate(
    models = map(.x = strap, ~lm(tmax ~ tmin + prcp, data = .x)), 
    results = map(models, broom::tidy)) |> 
  select(-strap, -models) |> 
  unnest(results) |> 
  group_by(term) |> 
  select(.id, term, estimate) |>
  pivot_wider(
    names_from = "term",
    values_from = "estimate"
  ) |> 
  janitor::clean_names() |>
  filter(tmin*prcp > 0) |> 
  mutate(
    log_B = log(tmin*prcp) 
  ) |> 
  summarize(
    LL = quantile(log_B, c(.025), na.rm = TRUE),
    UL = quantile(log_B, c(.975), na.rm = TRUE) 
  ) |> 
  ggplot(aes(x = log_B)) + geom_density() +
  labs(
    title = "Distribution of [simulated] log(b0*b1) values"
  )
```

Problem 3

Load and clean the data for regression analysis: 
```{r}
birthweight_data = 
  read_csv("birthweight.csv") |>  
  janitor::clean_names() |> 
  mutate(
    babysex = as.factor(babysex),
    frace = as.factor(frace),
    malform = as.factor(malform),
    mrace = as.factor(mrace)
  )
```

Propose a regression model for birthweight: 

```{r}
fit_birthweight = lm(bwt ~ smoken + pnumlbw + momage, data = birthweight_data)
fit_birthweight |>  broom::tidy()
```

show a plot of model residuals against fitted values – use add_predictions and add_residuals in making this plot: 

```{r}

```

